Causal Inference with Graphical Neural Networks

### 2024-04-11 latex/draft.tex
Pushing changes to latex file.

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{ntheorem}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\usepackage{tkz-graph}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes.geometric}

@@

\section{Introduction}

\section{Graph Neural Networks}

@@

\section{$\textbf{do}$ Operator}

@@

\section{Data}

@@

@@

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{ntheorem}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\usepackage{tkz-graph}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes.geometric}
\usepackage{hyperref}

@@

\section{Introduction}
\label{intro}

\section{Graph Neural Networks}
\label{gnn}

@@

\section{$\textbf{do}$ Operator}
\label{do}

@@

\section{Data}
\label{data}

@@

Each node of the graph was is associated with a specific conditional probability that the
creators of the dataset used to generate the data. These probabilities can be found in Table~\ref{tab:lucas_probs}
in Appendix~\ref{create}.

@@

\newpage

\section*{Appendix}

\appendix
\section{Creating the LUCAS0 Dataset}
\label{create}

As described in the \nameref{data} section, the LUCAS0 dataset is a toy dataset generated 
artificially by causal Bayesian networks with binary variables. The dataset consists of 
11 nodes and 2000 training samples. The causal diagram for the LUCAS0 dataset is shown in Figure~\ref{fig:lucas_dag}.

On the website, the authors mention that each node of the graph is associated with conditional probabilities
which were used to generate the data. These probabilities are found in Table~\ref{tab:lucas_probs}.

\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Conditional Probabilities}} \\
        \hline
        \textit{Conditional} & \textit{Probability} \\
        \hline
        P(Anxiety=T) & 0.64277 \\ \hline
        P(Peer Pressure=T) & 0.32997 \\ \hline
        P(Smoking=T|Peer Pressure=F, Anxiety=F) & 0.43118 \\ \hline
        P(Smoking=T|Peer Pressure=T, Anxiety=F) & 0.74591 \\ \hline
        P(Smoking=T|Peer Pressure=F, Anxiety=T) & 0.8686 \\ \hline
        P(Smoking=T|Peer Pressure=T, Anxiety=T) & 0.91576 \\ \hline
        P(Yellow Fingers=T|Smoking=F) & 0.23119 \\ \hline
        P(Yellow Fingers=T|Smoking=T) & 0.95372 \\ \hline
        P(Genetics=T) & 0.15953 \\ \hline
        P(Lung cancer=T|Genetics=F, Smoking=F) & 0.23146 \\ \hline
        P(Lung cancer=T|Genetics=T, Smoking=F) & 0.86996 \\ \hline
        P(Lung cancer=T|Genetics=F, Smoking=T) & 0.83934 \\ \hline
        P(Lung cancer=T|Genetics=T, Smoking=T) & 0.99351 \\ \hline
        P(Attention Disorder=T|Genetics=F) & 0.28956 \\ \hline
        P(Attention Disorder=T|Genetics=T) & 0.68706 \\ \hline
        P(Born an Even Day=T) & 0.5 \\ \hline
        P(Allergy=T) & 0.32841 \\ \hline
        P(Coughing=T|Allergy=F, Lung cancer=F) & 0.1347 \\ \hline
        P(Coughing=T|Allergy=T, Lung cancer=F) & 0.64592 \\ \hline
        P(Coughing=T|Allergy=F, Lung cancer=T) & 0.7664 \\ \hline
        P(Coughing=T|Allergy=T, Lung cancer=T) & 0.99947 \\ \hline
        P(Fatigue=T|Lung cancer=F, Coughing=F) & 0.35212 \\ \hline
        P(Fatigue=T|Lung cancer=T, Coughing=F) & 0.56514 \\ \hline
        P(Fatigue=T|Lung cancer=F, Coughing=T) & 0.80016 \\ \hline
        P(Fatigue=T|Lung cancer=T, Coughing=T) & 0.89589 \\ \hline
        P(Car Accident=T|Attention Disorder=F, Fatigue=F) & 0.2274 \\ \hline
        P(Car Accident=T|Attention Disorder=T, Fatigue=F) & 0.779 \\ \hline
        P(Car Accident=T|Attention Disorder=F, Fatigue=T) & 0.78861 \\ \hline
        P(Car Accident=T|Attention Disorder=T, Fatigue=T) & 0.97169 \\ \hline
        \hline
    \end{tabular}
    \caption{Conditional probabilities for the nodes in the LUCAS0 dataset.}
    \label{tab:lucas_probs}
\end{table}
